The abundance of Bullet-Groups in $\Lambda$CDM

### 2014-03-20 paper/ms.tex
conclusions

In this Letter we estimate the fraction of galaxy groups and clusters that
can present observational features associated to a bullet-like
event. This is motivated by the recent observational results of
\citep{Gastaldello} where a system (\bullg) on the mass range $1\times
10^{14}$\hMsun\ and velocity dispersion $650$\kms was reported to
feature a displacement between its baryonic (hot gas) and dark matter
components.

@@

Our main results is that that a fraction of $40\%$-$60\%$ of the halos
in the group sample present displacement equal or larger than the
observed displacement for \bullg. For halos in the cluster sample this
fraction increases to $60\%$-$80\%$. We also derive an
estimate for the displacement between the DM and the baryonic
component. In the group sample $0.1\%$-$1.0\%$ of the halos show a
displacement equal or larger than  the  measurements of \bullg\ by
\citep{Gastaldello}. In the cluster sample this fraction rises to
$4\%$-$10\%$.

For the case of \bullg\ a fair comparison is achieved against cluster
sample, which has statistics dominated by objects of similar mass. In
a rough comparison using the selection criteria by \citep{Gael2013,
  Gastaldello} we find that the relative number of bullet groups and
systems with large DM-DM displacements is consistent with
observations; both are in the range $\sim 7\%$. In terms of absolute
numer densities, we expect $\sim 6.0\times 10^{-7}$ Mpc$^{-3}$ Bullet
groups similar to \bullg; three times the expected value for Bullet
clusters.

We conclude that a new observational possibility opens up with surveys
such as SL2S that targett a large number of groups and estimate its
multi-modal nature from lensing analysis \citep{Foex2013}, an approach
that can be exploited with upcoming lensing surveys (e.g. with the
{\it Euclid} satellite).

>>>>

In this Letter we estimate the fraction of galaxy groups and clusters
in a $\Lambda$CDM cosmology that could present observational features
associated to a bullet-like event. This is motivated by the recent
observational results of \citep{Gastaldello} where a system (\bullg)
on the mass range $1\times 10^{14}$\hMsun\ and velocity dispersion
$650$\kms was reported to feature a displacement between its baryonic
(hot gas) and dark matter components.

@@

Our main result is that a fraction of $40\%$-$60\%$ of the halos
in the group sample present DM-DM displacement equal or larger than the
observed displacement for \bullg. For halos in the cluster sample this
fraction increases to $60\%$-$80\%$. We also derive an
estimate for the DM-baryon displacement In the group sample
$0.1\%$-$1.0\%$ of the halos show a displacement equal or larger than
the  measurements of \bullg\ by \citep{Gastaldello}; in the cluster
sample this fraction rises to $4\%$-$10\%$.

For the case of \bullg\ a fair comparison is achieved against our cluster
sample which has statistics dominated by objects of similar mass. In
a rough comparison using the selection criteria in \citep{Foex2013,
  Gastaldello} we find that the relative number of bullet groups
(large DM-baryon displacement) with respect to a general sample of
multi-modal systems (large DM-DM displacements) is consistent with
observations; both are in the range $\sim 7\%$.

In terms of absolute numer densities, we expect to have $\sim 6.0\times
10^{-7}$ Mpc$^{-3}$ groups similar to \bullg; three times the expected
value for clusters. This opens up a new observational possibility with surveys
such as SL2S that target a large number of groups and estimate its
multi-modal nature from lensing analysis \citep{Foex2013}. An approach
that can be further exploited with upcoming lensing surveys (e.g. with
the {\it Euclid} satellite).
